## Exploratory data analysis

```{r indicators}
lapply(config$sources,
			 function(source) {
			 	lapply(source$indicator,
			 				 function(indicator) {c("Dataset" = source$description, "Indicator" = indicator)}
			 	) %>% 
			 		dplyr::bind_rows()
			 }) %>% 
	dplyr::bind_rows() %>% 
	knitr::kable(caption = "List of indicators collected",
							 escape = TRUE) %>% 
	kableExtra::collapse_rows(valign = "top") %>% 
	kableExtra::kable_styling()
```

The indicators collected are listed in Table \@ref(tab:indicators).

### Outcome data

```{r}
death_rate <- outcome %>% 
	dplyr::filter(variable == "death_rate") %>% 
	tidyr::pivot_wider(id_cols = fips,
										 names_from = variable,
										 values_from = estimate)
```

```{r mort-hist, fig.cap="Distribution of infant mortality rate"}
ggplot(death_rate, aes(x = death_rate)) +
	geom_histogram(bins = 10, fill = config$colors$darkblue, alpha = 0.9) +
	theme_minimal() +
	labs(x = "Death rate per 100,000 births",
			 y = "Number of counties",
			 title = "Distribution of infant mortality rate")
```

In Figure \@ref(fig:mort-hist), we can see the generally normal distribution of the infant mortality rate by county. Furthermore, we can see that some counties have a very high infant mortality rate of almost `r scales::percent(max(death_rate$death_rate)/config$rate)`.

```{r included-counties, include=FALSE, fig.cap="Charts of counties included in sample"}
geo_county <- urbnmapr::get_urbn_map("counties", sf = TRUE)

included_map <- geo_county %>% 
	dplyr::left_join(death_rate, by = c("county_fips" = "fips")) %>% 
	ggplot(aes(fill = death_rate)) +
	geom_sf(color = "#ffffff", size = 0.05) +
	theme_minimal() +
	theme(axis.text = element_blank(),
				panel.grid = element_blank()) +
	scale_fill_gradient(low = config$colors$lightblue,
											high = config$colors$darkblue,
											na.value = config$colors$gray) +
	labs(title = "Counties included in sample",
			 fill = "Death rate")

all_pop <- tidycensus::get_acs(geography = "county", variables = "B01001_001") %>% 
	dplyr::select(fips = GEOID, population = estimate) %>% 
	dplyr::left_join(outcome %>% 
									 	dplyr::select(fips) %>% 
									 	dplyr::distinct() %>% 
									 	dplyr::mutate(Included = "Yes")) %>% 
	dplyr::mutate(Included = tidyr::replace_na(Included, "No")) %>% 
	ggplot(aes(x = log(population), y = 1, color = Included)) +
	ggbeeswarm::geom_quasirandom(groupOnX = FALSE, size = 2.5, alpha = 0.75) +
	theme_minimal() +
	labs(x = "Population (log)",
			 title = "Population distribution",
			 subtitle = "All US counties") +
	theme(axis.title.y = element_blank(),
				axis.text.y = element_blank()) +
	scale_color_manual(values = c("Yes" = config$colors$darkblue, "No" = config$colors$gray))

gridExtra::grid.arrange(included_map, all_pop, nrow = 1)
```

```{r map, fig.cap="Map of infant mortality rate by county"}
included_map
```

```{r pop, fig.cap="Population for all counties in the United States"}
all_pop +
	labs(title = "Distribution of logged population, all US counties",
			 subtitle = NULL)
```

Figure \@ref(fig:map) shows the counties included in the study, filled by their infant mortality rate, and Figure \@ref(fig:pop) shows the distribution of the population of all counties in the US, colored by their inclusion in the study. Because the CDC suppresses data from counties with too few infant deaths, the sample represents mostly high-population counties. The missing counties almost certinaly influence the results, as many in the West, North, and Midwest are rural, overwhelmingly White counties; additionally, many of the missing counties in the Deep South have large Black populations which may face different conditions than Black populations on the coasts.

### Demographic data

```{r corrplot, fig.cap="Correlation plot for indicators under consideration"}
demographics %>%
	dplyr::select(fips, variable_name_short, estimate) %>%
	tidyr::pivot_wider(names_from = "variable_name_short", values_from = "estimate") %>%
	dplyr::select(-fips) %>%
	cor(.) %>%
	ggcorrplot::ggcorrplot(type = "full") +
	theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

In Figure \@ref(fig:corrplot) we can see the correlations between our different demographic indicators. There are some obvious correlations due to singularities, such as between male and female. There are important correlations to consider across types of indicators, such as insurance and income, race, and education; education and income and race; and food stamps and income. We can use interaction terms in the regression to account for this.

```{r food-stamps-income, eval=FALSE, fig.cap="There is a strong negative correlation between food stamps and income"}
demographics %>%
	dplyr::select(fips, variable_name_short, estimate) %>%
	dplyr::filter(variable_name_short %in% c("food_stamp", "income")) %>%
	tidyr::pivot_wider(id_cols = fips,
										 names_from = "variable_name_short",
										 values_from = "estimate") %>%
	ggplot(aes(x = food_stamp, y = income)) +
	geom_point() +
	theme_minimal() +
	labs(x = "Rate of residents on food stamps",
			 y = "Median income",
			 title = "Correlation between income and food stamps") +
	scale_x_continuous(labels = scales::comma) +
	scale_y_continuous(labels = scales::comma)
```

Before regression, all relevant demographic variables were transformed into rates using the county's population. Both the infant mortality rate and the demographic variables are expressed in per-$`r scales::comma(config$rate)$ levels.

