## Data analysis

### Variable selection

```{r}
df_fit <- df %>% 
	dplyr::select(-fips, -female, -under_18, -insured, -population)

fit_int <- lm(death_rate ~ 1, data = df_fit)
fit_full <- lm(death_rate ~ ., data = df_fit)
fit_interactions <- lm(death_rate ~ . + food_stamp*income + uninsured*income +
											 uninsured*black + uninsured*hispanic + uninsured*white + uninsured*asian +
											 uninsured*less_HS + uninsured*complete_HS + uninsured*some_college + uninsured*college +
											 income*less_HS + income*complete_HS + income*some_college + income*college +
											 income*black + income*hispanic + income*white + income*asian,
											 data = df_fit)

best_full <- step(fit_int, scope = list(lower = fit_int, upper = fit_full), direction = "forward", trace = 0)
best_interaction <- step(fit_int, scope = list(lower = fit_int, upper = fit_interactions), direction = "forward", trace = 0)
```

First, we set our models. The base model is of the form $y_i = \beta_0$. The full model looks like $y_i = \beta_0 + \beta_1x_{i,1} + \cdots + \beta_{`r ncol(df_fit)`}x_{i,`r ncol(df_fit)`}$. Finally, we also test a full model with interactions between insurance and income, race, and education; and income and education and race.

We can use forward stepwise selection to find the model with the lowest $\mathrm{AIC}$ score.

When comparing the full model to the base model, the best model is `r print_latex_equation(best_full)`

When comparing the model with interactions to the base model, the best model is `r print_latex_equation(best_interaction)`

The $\mathrm{AIC}$ of the model with interactions is lower than that of the model without interactions, so we'll use the one with interactions.

### Model diagnostics

We also need to examine the diagnostic plots to determine whether multiple linear regression is suitable for these data.

```{r fitted-residual, fig.cap="Residual vs fitted value plot"}
ggplot(fit, aes(x = .fitted, y = .resid)) +
	geom_point() +
	theme_minimal() +
	labs(title = "Residual vs fitted value plot",
			 x = "Fitted value",
			 y = "Residual")
```

Figure \@ref(fig:fitted-residual) shows a residual-fitted value plot. There is no discernible pattern, which suggests linearity constant variance of the errors.

```{r qq, fig.cap="Normal QQ plot for the residuals"}
ggplot(fit, aes(sample = .resid)) +
	geom_qq() +
	geom_qq_line() +
	theme_minimal() +
	labs(x = "Theoretical quantile",
			 y = "Sample quantile",
			 title = "Normal QQ plot for the residuals")
```

Figure \@ref(fig:qq) shows a Normal QQ plot of the residuals, which in this case suggests a general normality of the errors. There are a few points at the tails which could raise some concern, but the pattern is roughly linear.

```{r scale-location, fig.cap="Scale-location plot"}
ggplot(fit, aes(x = .fitted, y = .stdresid)) +
	geom_point() +
	theme_minimal() +
	labs(x = "Fitted values",
			 y = "Standardized residuals",
			 title = "Scale-Location plot")
```

Figure \@ref(fig:scale-location) shows the standardized residuals versus the fitted values. Again, we do not see much of a pattern.

```{r resid-leverage, fig.cap="Residuals vs leverage plot"}
ggplot(fit, aes(x = .hat, y = .stdresid)) +
	geom_point() +
	geom_vline(xintercept = 4*ncol(fit$model)/nrow(fit$model)) +
	geom_hline(yintercept = c(2, -2)) +
	theme_minimal() +
	labs(x = "Leverage",
			 y = "Standardized residuals",
			 title = "Residuals vs leverage")
```

Finally, Figure \@ref(fig:resid-leverage) shows the standardized residuals versus leverage. There are a few outliers with low leverage and a few leverage points with small residuals, and there is one point that is barely a leverage point by our $4p/n$ cutoff that is an outlier, i.e. a bad leverage point.

All together, these diagnostics suggest that a MLR model is adequate for these data.

### Regression results

```{r reg}
fit <- lm(best_interaction$call$formula, data = df_fit)

papeR::prettify(summary(fit)) %>% 
	dplyr::mutate(dplyr::across(2:6, ~round(., 5))) %>% 
	dplyr::select(-ncol(.)) %>% 
	knitr::kable(caption = "Regression output for best model") %>% 
	kableExtra::kable_styling()
```

Table \@ref(tab:reg) shows the summary table of this regression. 
