## Data analysis

### Variable selection

```{r}
df_fit <- df %>% 
	dplyr::mutate(other_race = config$rate - (white + black + hispanic + asian)) %>% 
	dplyr::select(-fips, -female, -under_18, -insured, -white)

fit_int <- lm(death_rate ~ 1, data = df_fit)
fit_full <- lm(death_rate ~ ., data = df_fit)
# fit_interactions <- lm(death_rate ~ . + food_stamp*income + uninsured*income +
# 											 uninsured*black + uninsured*hispanic + uninsured*white + uninsured*asian +
# 											 uninsured*less_HS + uninsured*complete_HS + uninsured*some_college + uninsured*college +
# 											 income*less_HS + income*complete_HS + income*some_college + income*college +
# 											 income*black + income*hispanic + income*white + income*asian,
# 											 data = df_fit)

best_full <- step(fit_int, scope = list(lower = fit_int, upper = fit_full), direction = "forward", trace = 0)
best_full_fit <- lm(best_full$call$formula, data = df_fit)

fit_interactions <- lm(death_rate ~ income + black + hispanic + other_race + gini + some_college + male +
											 	income*black + income*hispanic + income*other_race +
											 	income*gini + income*some_college +
											 	some_college*black + some_college*hispanic + some_college*other_race,
											 data = df_fit)

best_interaction <- step(best_full_fit, scope = list(lower = best_full_fit, upper = fit_interactions), direction = "forward", trace = 0)

fit <- lm(best_full$call$formula, data = df_fit)
```

First, we set our models. The base model is of the form $y_i = \beta_0$. The full model looks like $y_i = \beta_0 + \beta_1x_{i,1} + \cdots + \beta_{`r ncol(df_fit)`}x_{i,`r ncol(df_fit)`}$. We can use forward stepwise selection to find the model with the lowest $\mathrm{AIC}$ score. When comparing the full model to the base model, the best model is `r print_latex_equation(best_full)`

Then, we can expand upon the full model by including some interactions, namely between income and race, income and the Gini index, income and education, and education and race. When comparing the expanded model with interactions to the best full model, the best model with interactions is `r print_latex_equation(best_interaction)`

The $\mathrm{AIC}$ of the best model without interactions is $`r round(AIC(best_full))`$, and the $\mathrm{AIC}$ of that model with added interactions is $`r round(AIC(best_interaction))`$. Because these are practically identical, the interactions do not have a practically significant effect, so it is valid to choose the model without interactions.

### Model diagnostics

We also need to examine the diagnostic plots to determine whether multiple linear regression is suitable for these data.

```{r diag, fig.cap="Diagnostic plots"}
resfit <- ggplot(fit, aes(x = .fitted, y = .resid)) +
	geom_point() +
	theme_minimal() +
	labs(title = "Residual vs fitted value plot",
			 x = "Fitted value",
			 y = "Residual")

qq <- ggplot(fit, aes(sample = .resid)) +
	geom_qq() +
	geom_qq_line() +
	theme_minimal() +
	labs(x = "Theoretical quantile",
			 y = "Sample quantile",
			 title = "Normal QQ plot for the residuals")

scale_location <- ggplot(fit, aes(x = .fitted, y = .stdresid)) +
	geom_point() +
	theme_minimal() +
	labs(x = "Fitted values",
			 y = "Standardized residuals",
			 title = "Scale-Location plot")

resid_leverage <- ggplot(fit, aes(x = .hat, y = .stdresid)) +
	geom_point() +
	geom_vline(xintercept = 4*ncol(fit$model)/nrow(fit$model)) +
	geom_hline(yintercept = c(2, -2)) +
	theme_minimal() +
	labs(x = "Leverage",
			 y = "Standardized residuals",
			 title = "Residuals vs leverage")

gridExtra::grid.arrange(resfit, qq, scale_location, resid_leverage,
												nrow = 2)
```

Figure \@ref(fig:diag) shows the diagnostic plots for the MLR model. There is no discernible pattern in the residual-fitted value plot, which suggests linearity constant variance of the errors. Further, the linearity of the normal QQ plot of the residuals suggests a general normality of the errors. There are a few points at the tails which could raise some concern, but the pattern is roughly linear. The scale-location plot shows the standardized residuals versus the fitted values. Again, we do not see much of a pattern. Finally, the standardized residuals versus leverage plot shows leverage points and outliers. There are a few outliers with low leverage and a few leverage points with small residuals, and there is one point that is barely a leverage point by our $4p/n$ cutoff that is an outlier, i.e. a bad leverage point.

All together, these diagnostics suggest that a MLR model is adequate for these data.

### Regression results

```{r reg}
papeR::prettify(summary(fit)) %>% 
	dplyr::mutate(dplyr::across(2:6, ~round(., 5))) %>% 
	dplyr::select(-ncol(.)) %>% 
	knitr::kable(caption = "Regression output for best model") %>% 
	kableExtra::kable_styling()
```

Table \@ref(tab:reg) shows the summary table of this regression. An increase in the county's median income, the proportion of Hispanic residents, and the Gini index of inequality all have statistically significant substantial negative effects on the infant mortality rate, while the proportion of Black residents and the proportion of residents of other race have statistically significant positive substantial effects on the infant mortality rate.
